The pollination trade-off

### 2018-11-27 paper/manuscript.Rmd
Rename chunk of facilitation slopes
Update figure 1 caption

```{r facilitation-stats, echo = F}
drake::loadd(facilitation_plot_df)

@@

```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen. Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models). The horizontal and vertical bars under each dot indicate the 0.05 bootstrap confidence intervals of the estimates. The solid lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al. 2012). The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}
# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
# pdf(width = 6.5, height = 4)
drake::loadd(fig_random_slopes)
drake::loadd(fig_con_con)
drake::loadd(fig_hetero_con)
width_left <- 6.5*3/5
bar_plot_width <- 0.325
rw <- c(width_left - bar_plot_width,
        bar_plot_width, 
        6.5 - width_left - bar_plot_width,
        bar_plot_width)
left <- cowplot::plot_grid(
  fig_hetero_con,
  NULL,
  fig_con_con[[1]],
  fig_con_con[[2]],
  ncol = 2, 
  rel_widths = rw[c(3,4)], 
  align = "h"
)
right <- cowplot::plot_grid(
  fig_random_slopes[[1]],
  fig_random_slopes[[2]], 
  ncol = 2, 
  align = "h", 
  rel_widths = rw[1:2]
)
cowplot::plot_grid(
  right,
  left,
  ncol = 2,
  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
)
# dev.off()
```

>>>>

```{r facilitation-random-model-stats, echo = F}
drake::loadd(facilitation_plot_df)

@@

```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "**Competition vs. facilitation at the community level**. (a) Some species experience more competition for pollination than others. Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities. Negative slopes indicate that plants experience competition for animal-mediated pollination, while positive slopes indicate that facilitation is the predominant outcome. The number of of plants analised for each species is shown within brakets next to the species name. (b) Despite the variety of slopes, overall plants had have more conspecific than heterospecific pollen deposited in their stigmas. (c) Generally, plants also had more pollen depositied in their stigmas when they were open to animal-mediated pollination than when they were closed. However in the majority of cases the difference is not large enough to be statistically significant at the 0.05 level. In all plots, erro bars correspond to ± the standard error (SE)."}
# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
# pdf(width = 6.5, height = 4)
drake::loadd(fig_random_slopes)
drake::loadd(fig_con_con)
drake::loadd(fig_hetero_con)
width_left <- 6.5*3/5
bar_plot_width <- 0.325
rw <- c(width_left - bar_plot_width,
        bar_plot_width, 
        6.5 - width_left - bar_plot_width,
        bar_plot_width)
left <- cowplot::plot_grid(
  fig_hetero_con,
  NULL,
  fig_con_con[[1]],
  fig_con_con[[2]],
  ncol = 2, 
  rel_widths = rw[c(3,4)], 
  align = "h"
)
right <- cowplot::plot_grid(
  fig_random_slopes[[1]],
  fig_random_slopes[[2]], 
  ncol = 2, 
  align = "h", 
  rel_widths = rw[1:2]
)
cowplot::plot_grid(
  right,
  left,
  ncol = 2,
  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
)
# dev.off()
```
